A Test of the Frequency Independence Assumption of the System Parameters used in Geomagnetically Induced Current Calculations

### 2019-01-11 agujournaltemplate.tex
Updates from ShareLaTeX

>>>>

\begin{figure}[h]
\centering
\includegraphics[]{figures/plot_raw_All_20060402.pdf}
\caption{(Top) One-second-cadence geomagnetic field measured at the Memanbetsu Magnetic Observatory (MMB). (Middle) One-second-cadence geoelectric field measured at the Memanbetsu Magnetic Observatory (MMB) X km from the Memanbetsu substation. (Bottom) One-second-cadence GIC measurements measured in a grounded neutral point of a Y-connected three-phase transformer connected to a 187 kV bus at the Memanbetsu substation of the Hokkaido Power Co.}
\label{figure1}
\end{figure}
